Local Group Satellite Alignments

### 2017-07-18 paper/paper.tex
new figure

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
\caption{Halo pair samples used in this paper located in the
  plane of relative radial velocity $V_{r,AB}$ versus 
  distance $R_{AB}$ between the two halos in the pair.
  The IP sample (24 pairs) is a general pair sample, while the LGP
  sample (12 pairs) resemples the separation and kinematic
  conditions observed in the Local Group.} 
\label{fig:samples}
\end{figure}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.31\textwidth]{nsat.pdf}
\includegraphics[width=0.31\textwidth]{mstar.pdf}
\includegraphics[width=0.31\textwidth]{vmax.pdf}
\caption{Numer of satellites, stellar mass, vmax\label{fig:general}}
\end{figure*}
%\caption{Halo pair samples used in this paper located in the
%  plane of relative radial velocity $V_{r,AB}$ versus 
%  distance $R_{AB}$ between the two halos in the pair.
%  The IP sample (24 pairs) is a general pair sample, while the LGP
%  sample (12 pairs) resemples the separation and kinematic
%  conditions observed in the Local Group.}
